Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
added bug found

\emph{Results.}~\Fix{REVISE}We considered engines from four major players--Apple,
Google, Microsoft, and Mozilla. Our results indicate that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation{}
bugs (\noBugsTransplantationConfirmed{} confirmed) and differential
testing revealed \noBugsDifferentialTesting{} bugs
(\noBugsDifferentialTestingConfirmed{}). Furthermore, results indicate
that most of these bugs affected only two engines--Apple's \jsc{}
(\percJSC{}) and Microsoft's \chakra{} (\percChakra{}); we found only
one bug in Google \veight{} and none in Mozilla's \smonkey{}. Although
our experience indicates that more research needs be done to automate
parts of the inspection process, our results show that exploring
diversity is a valuable help to find bugs in JavaScript engines.

@@

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4.}\Mar{de que tabela?} The JS code \CodeIn{\{var a =
  \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}} manifested a bug in the \js{} engine \chakra{}.
The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the Radamsa fuzzer~\cite{radamsa}
returns a string representation of a null character (\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}",
used in the assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
  chakra did that it would be fine, no?} evaluates the unary
plus to NaN as expected, as the null character cannot be converted. As
result, the test fails as expected. \chakra{}, in contrast,
incorrectly converts the string to zero, making the test to pass. All
other engines fail on this test. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

@@

\begin{itemize}
  \item The diversity-aware techniques we used are great
    at finding bugs in \js\ engines;
  \item The cost of inpecting failures/warnings is high. Although the
    inspection activity was not uninterrupted, it is safe to say that
    each warning required a substantial amount of time to analyze for
    potential false alarms;
  \item We have found more bugs with test transplantation than we have
    with cross-engine differential testing. In addition, test
    transplantation demanded less effort per bug;
  \item Even simple black-box fuzzers can create surprisingly
    interesting inputs;
  \item Mozilla's \smonkey\ appears to be the most reliable
    \js\ engine we used, with Google's \veight\ after it;
  \item Reporting real bugs is a great way to train (and encourage)
    students in software testing.
\end{itemize}

>>>>

\emph{Results.}~\Fix{REVISE}We considered engines from four major players--Apple,
Google, Microsoft, and Mozilla. Our results indicate that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation{}
bugs (\noBugsTransplantationConfirmed{} confirmed, \noBugsTransplantationFixed{} fixed) and differential
testing revealed \noBugsDifferentialTesting{} bugs
(\noBugsDifferentialTestingConfirmed{} confirmed and \noBugsDifferentialTestingFixed{} fixed). Furthermore, results indicate
that most of these bugs affected only two engines--Apple's \jsc{}
(\percJSC{}) and Microsoft's \chakra{} (\percChakra{}); we found only
one bug in Google \veight{} and none in Mozilla's \smonkey{}. Although
our experience indicates that more research needs be done to automate
parts of the inspection process, our results show that exploring
diversity is a valuable help to find bugs in JavaScript engines.

@@

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:cross-testing}.} 
The JS code \CodeIn{\{var a =
  \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}} manifested a bug in the \js{} engine \chakra{}.
The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the Radamsa fuzzer~\cite{radamsa}
returns a string representation of a null character (\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}",
used in the assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
  chakra did that it would be fine, no?} evaluates the unary
plus to NaN as expected, as the null character cannot be converted. As
result, the test fails as expected. \chakra{}, in contrast,
incorrectly converts the string to zero, making the test to pass. All
other engines fail on this test. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

\vspace{1ex}\noindent\textbf{Issue \#16, Table~\ref{tab:cross-testing}.}
\Igor{
  Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
  Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
  que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
  de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
  that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
  B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
  function declaration. The fuzzer removes the function declaration and 
  injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
  the break statement should throw an early error (in this case a SyntaxError) 
  if the break statement is not nested in an iterational or a switch statement. All engines works
  as expected but \veight{} pass without failures.
}

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assert, assertEq, var, yield, in, function, eval,
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
// Original file
eval(
"{ 
    function f() { 
      return 'declaration'; 
    } 
 }
 assert.sameValue(typeof f, 'function');
 \assert.sameValue(f(), 'declaration');"
);
------------------------------------------
// Fuzzed file
eval(function b (a) {
  break;
});
  \end{lstlisting}
  \normalsize
  \caption{\label{fig:bug-veight}Fuzzed code mutated by \quickfuzz{}
  and reported in \veight{} engine}
\end{figure}

@@

\begin{itemize}
  \item The diversity-aware techniques we used in this study are great
    at finding bugs in \js\ engines;
  \item The cost of inpecting failures/warnings is high. Although the
    inspection activity was not uninterrupted, it is safe to say that
    each warning required a substantial amount of time to analyze for
    potential false alarms;
  \item Even simple black-box fuzzers can create surprisingly
    interesting inputs;
  \item Mozilla's \smonkey\ appears to be the most reliable
    \js\ engine, with Google's \veight\ after it;
  \item Reporting real bugs is a great way to train (and encourage)
    students in software testing.
\end{itemize}
